Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-02 acl.2016/response.txt

Thank you for reviewing our paper, the comments are very useful for us in correcting our paper. I'll try and respond to most of questions.

1. We will fix the numerous typos and difficult-to-read sentences all reviewers have pointed out.

2. We will add references to (Zens & Ney, 2008) and (Wuebker et al, 2012), and look at references to the Jane decoder.

3. Strangely, using lexicalised reordering model results in slightly faster decoding than without the model. We double checked with other datasets. We suspect this may be an artifact of the algorithm or datastructures, for example, more work is needed to resolve hypothesis recombination. We will endeavour to find the cause of this issue.

4. Two of the coverage curves in Figure 5 exactly overlap, we will make that clear in the paper.

5. All models in all experiments are read on-demand. The text phrase-table is 8.1GB zipped (40GB unzipped), the Lex RO is 3.5GB zipped (20GB unzipped), the LM is 3.1GB zipped (5.3GB unzipped). Furthermore, the decoder often requires multiple times the file sizes in RAM to hold the datastructures in memory.

For example, trying to load the phrase-table into memory took 67 minutes to load and decode and used over 200GB of virtual memory. Trying to load the phrase-table and re-ordering model into memory exhausted our 340GB server.

This compares to 3-4 minutes decoding time and approximately 30GB of virtual memory when on-demand models are used.

Therefore, even though it may be possible to load some models into RAM on our specific server, it is suboptimal and not advisable for most scenarios due to memory and/or time constraints. We will add these remarks to the paper.

6. We cache the 'most common source phrase' according to the count statistics obtained from the training data. We will make that clearer in the paper.

7. We will add a more detailed description of memory pools.

8. We will add a more detailed explanation of the different stack configurations and discussions. We also have further results which will include as it will be appropriate if the paper contains more discussion on the subject.

9. The speedup in our work was such that we could not accurately evaluate decoding speeds when measured on typical test sets which contains 1000-2000 sentences. Since decoding speed is not affected by whether it is decoding the training data, or held out data, we decoded the training data for convenience. We will test this assumption and add a remark in the paper. Where reporting model scores was necessary, we did, of course, used a held-out test set.

### 2016-05-02 acl.2016/acl2016.tex
changes after review

%
% File ACL2016.tex
%

@@

In this paper we re-assess the major components of phrase-based decoding and decoder implementation with particular emphasis on speed and scalability on multicore machines. The result is a drop-in replacement for the Moses decoder which is up to fifteen times faster and scales almost linearly with the number of cores.

@@

SMT has steadily progressed from a research discipline to public useability during the past decade via services such as Google Translate, Microsoft Translator Hub, as well as products and services for customized translation such as those from Language Weaver and the open-source Moses toolkit. The latter has spawned a cottage industry ranging from small language service providers seeking to reduce translation cost, to large inter-govermental agencies such as the EU and the UN that require high volume, in-house machine translation.

For high volume users, decoding is a most time critical part of the translation process. A common strategy to increase decoding throughput is to make use of the multiple cores that are now ubiquitous in todays servers. However, it has been noticed that the Moses decoder, amongst others, is unable to efficiently use multiple~\cite{mfernandez2016boosting}. That is, decoding speed does not substantial increase when more cores are used, in fact, it may actually \emph{decrease} when more cores are added.

There have be speculation on the causes of the inefficiency as well as potential remedies. This paper is the first we know of that seeks to tackle this problem head on. We present an phrase-based decoder that is not only significantly faster than the Moses baseline for single-threaded operation, but is able to run multiple threads on multicore machines with only a slightly loss in linear speed. Model scores and functionality are compatible with Moses to aid comparison and ease transition for users. All source code will be made available under an open-source license.

@@

There are a number of open-source SMT projects, most includes a decoder. The most well known is Moses~\cite{koehn-EtAl:2007:PosterDemo}, which supports phrase-based models, hierarchical phrase-based as well as various syntax-based models. Joshua~\cite{Joshua-Decoder} also supports hierarchical and syntax models and has recently supported phrase-based models. Phrasal supports a number of variants of the phrase-based model. CDEC~\cite{dyer2010cdec} supports hierarchical and syntactic models.

A number of the decoders support multithreading whilst others use alternative methods such as Hadoop or external scripts to parallelize decoding.

>>>>

% Jane - FastSCSS single-best output, but is considerably faster by not maintaining separate model costs and by deleting recombined hypotheses
% Jane - not multithreaded
% Zens & Ney - don't compare different coverage config. Not focused on speed.
%
% File ACL2016.tex
%

@@

In this paper we re-examining the major components of phrase-based decoding and decoder implementation with particular emphasis on speed and scalability on multicore machines. The result is a drop-in replacement for the Moses decoder which is up to fifteen times faster and scales monotonically with the number of cores.

@@

SMT has steadily progressed from a research discipline to commercial viability during the past decade as can be seen from services such as the Google and Microsoft Translation services. As well as general purpose services such as these, there is a large number of companies that offer customized translation systems, as well as  companies and organization that implement in-house solutions. Many of these customized solutions use Moses as their SMT engine.

For many users, decoding is the most time-critical part of the translation process. Making use of the multiple cores that are now ubiquitous in todays servers is a common strategy to ameliorate this issue. However, it has been noticed that the Moses decoder, amongst others, is unable to efficiently use multiple cores~\cite{mfernandez2016boosting}. That is, decoding speed does not substantially increase when more cores are used, in fact, it may actually \emph{decrease} when using more cores. There have be speculation on the causes of the inefficiency as well as potential remedies.

This paper is the first we know of that focuses on improving decoding speed on multicore servers. We will take a holistic approach to solving this issue, re-implementing the decoder's structure to optimize for speed, re-assessing some of the optimization assumptions made in the implementation of significant parts of the decoder, as well as exploring changes to the core search algorithm. We will compare and contrast decoder implementations, not just decoding algorithms or individual components.

We will present a phrase-based decoder that is significantly faster than the Moses baseline for single-threaded operation, and scales monotonically with the number of cores.

As far as possible, model scores and functionality are compatible with Moses to aid comparison and ease transition for existing users. All source code will be made available under an open-source license.

@@

There are a number of phrase-based decoding implementations, we shall detail some of the open-source implementations.

The most well known is Moses~\cite{koehn-EtAl:2007:PosterDemo} which supports phrase-based models, hierarchical phrase-based as well as various syntax-based models. It is widely used for MT research and commercial use.

Joshua~\cite{Joshua-Decoder} also supports hierarchical and syntax models and has recently supported phrase-based models. Phrasal~\cite{spence2014phrasal} supports a number of variants of the phrase-based model. Jane~\cite{peitz2012jane} supports hierarchical and standard phrase-based models. mtplz~\newcite{Heafield-mtplz} implements an speed-optimized variant of the phrase-based search algorithm.

The Moses, Joshua and Phrasal decoders implement multithreading, while Jane uses an external application to parallelize operation. All the multi-threaded implementations report scalability problems, either in the paper (Phrasal) or via social media (Moses\footnote{https://github.com/moses-smt/mosesdecoder/issues/39} and Joshua\footnote{https://twitter.com/ApacheJoshua/status/342022794097340416}).
